---
title: "Supplemetary materials to Part 2 -- Integrating the Two Disparate Research Streams"
#author: "Miao Cai <miao.cai@slu.edu>"
date: "1/5/2020"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: yes
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      eval = FALSE,
                      fig.width = 8, 
                      fig.height = 8*0.418)
```

This GitHub page website serves as the supplementary materials for the manuscript *Bridging the Gap between Optimization and Statistical Modeling of Large Truck Safety: A Review -- Part 2: Prescriptive Modeling and an Example Integrating the Two Disparate Research Streams*, submitted to [Sensors](https://www.mdpi.com/journal/sensors).


Simulating risk data
====================
The Python code to simulate risk data can be found in [this](01Simulating risk data.html) Jupyter Notebook.


Statistical modeling
====================
The Python code to perform statistical modeling can be found in [this](02Statistical_modeling.html) Jupyter Notebook. Four statistical models were considered in this example:

  + logistic regression
  + Poisson regression
  + XGBoost
  + neural networks

Optimization
============
The Python code to perform optimization can be found in [this](03Optimization.html) Jupyter Notebook.

<!--
Simulating risk data
====================
```{r, echo=FALSE}
htmltools::includeHTML("01Simulating risk data.html")
```

Statistical modeling
====================

```{r, echo=FALSE}
htmltools::includeHTML("02Statistical_modeling.html")
```

Optimization
============

```{r, echo=FALSE}
htmltools::includeHTML("03Optimization.html")
```
-->

Concordance plot
================
We also include a concordance plot to show the prediction results in different models. The R code to reproduce the plot can be found below:

```{r eval=T}
pacman::p_load(dplyr, ggplot2, data.table, tidyr, ggthemes, viridis, showtext)

d = data.table::fread("data/lk_risks.csv") %>% 
  mutate(path = paste(`Node A`, `Node Z`, sep = "-") %>% 
           gsub("node ", "", .)) %>% 
  select(path, starts_with("risk_")) %>% 
  mutate_each(function(x)dense_rank(desc(x)), -path) %>% 
  arrange(risk_logit) %>% 
  mutate(path = factor(path, levels = .$path)) %>% 
  pivot_longer(cols = risk_logit:risk_DL, 
               names_to = "stats model", 
               values_to = "risk rank") %>% 
  mutate(`stats model` = gsub("risk_", "", `stats model`)) %>% 
  mutate(`stats model` = case_when(`stats model` == "logit" ~ "Logistic",
                                   `stats model` == "poisson" ~ "Poisson",
                                   `stats model` == "xgboost" ~ "XGBoost",
                                   `stats model` == "DL" ~ "Deep Learning") %>% 
           factor(levels = c("Logistic", "Poisson", "XGBoost", "Deep Learning")))
```

```{r eval=T}
d %>% 
  ggplot(aes(x = path, y = `stats model`, fill = `risk rank`)) + 
  scale_fill_viridis(option="magma", 
                     breaks = c(1, 5, 10, 15, 20), 
                     guide = guide_legend(reverse = FALSE)) + 
  geom_tile(color = "white") + 
  xlab("Path: node A - node Z") + 
  theme_tufte(ticks = F) + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(hjust = 1),
        panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.text.x = element_text(margin = margin(t = -2, r = 0, b = 0, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = -3, b = 0, l = 0),
                                   hjust = 0)) 
```

